Highly Available Transactions: Virtues and Limitations

### 2013-03-31 writeup/conclusion.tex
Respin

\section{Conclusion}

In this paper, we have begun to understand the relationship between
multi-operation, multi-object transactions and high availability. We
have outlined requirements for high availability in a transactional
context, or Highly Available Transactions (HATs) and taxonomized
guarantees spanning both distributed systems and ACID database
literature accordingly. Many transactional guarantees are achievable
with high availability, while a few, like preventing Lost Update and
Write Skew, are not. To understand the benefits of high availability
and low latency, we classified the prevalence and cost of partitions
and network latency both in the literature and via experiment, while
analyzing existing transactions to determine whether HATs were
sufficient to ensure application consistency.

Fundamentally, high availability represents a new constraint for
database designs. While the CAP Theorem has had a large impact on
highly available distributed data storage design, our knowledge of
database systems has not kept pace. The key distributed systems
challenge of designing distributed algorithms and architectures for
partial failure and network asynchrony is largely unaddressed in the
literature on transaction processing systems. To fully realizing the
potential of HAT systems will require further rearchitecture and study
of existing database designs as well as better understanding of
application semantics and their relationship to distributed
consistency.

>>>>

\section{Conclusion}
The current state of database software offers uncomfortable and unnecessary
choices between availability and transactional semantics.
In this paper we expose a broad design space of Highly Available Transactional 
Systems (HATs), which can offer the key benefits of
highly available distributed systems---partition tolerance and low-latency 
writes---while also providing a family of transactional isolation 
levels and replica semantics that have been widely used in practice. 
In taxonomizing this design space, we show that many transactional 
guarantees are achievable with high availability, while a few, 
like preventing Lost Update and Write Skew, are not.

There has been some debate in the database community regarding the importance
of availability in modern databases; there is also concern about the utility of
relaxed isolation.  Our analysis and experiments in Sections~\ref{sec:motivation} 
and~\ref{sec:evaluation} convince us that the availability goals of the NoSQL
movement will remain a critical aspect of many important systems going forward, and 
that the isolation levels available via HATs can have significant practical impact
in delivering useful transactional semantics to application developers.

Much of the prior research in distributed transactions has focused on prototyping 
individual points in the design space, with a focus on providing serializability
at the expense of availability.  Our goal in this paper has been to take a broader view. 
We taxonomize the joint design space of replica consistency and transactional isolation,
and identify what is possible and impossible to achieve semantically via HATs.  From
a research perspective, this offers a long-overdue connection between storage 
semantics studied in the database and distributed systems communities.
With this understanding in hand, the next challenge is to return to issues of 
performance and systems architecture within the HATs design space.  Based on our 
understanding of what is desired in the field and what is possible to achieve, we 
believe this is an area of great opportunity in the coming years.
